### 2020-04-16 preamble.tex
add lots more figures

\RequirePackage{luatex85, shellesc} % work around the LuaTex bug
% options for packages which may be loaded elsewhere
\PassOptionsToPackage{unicode=true, pdfa}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}

%==============================================================================%
%                                Load packages                                 %
%==============================================================================%

\usepackage{amsmath}                  % the AMS Math package - provides useful math environments and tools

\usepackage{amssymb}                  % provides useful symbols

\usepackage{amsfonts}                 % provides nice mathematical fonts

\usepackage{bm}                       % bold math

\usepackage{calc}                     % gives the ability to calculate in the document itself, inferior to but lighter weight than pythontex

\usepackage{cancel}                   % provides environments to cancel stuff in mathmode

\usepackage{esint}                    % better and more integral signs

\usepackage{enumitem}                 % enumerate and itemize improvements

\usepackage{fancyhdr}                 % fancy headers and footers

\usepackage[vario]{fancyref}          % for fancy cross-referencing with vario-style refs

\usepackage{graphicx}                 % facilitates inclusion of external graphics

\usepackage{microtype}                % typographical improvements, kerning, etc

\usepackage{parskip}                  % produces zero \parindent and non-zero \parskip

\usepackage{setspace}                 % set space between lines

\usepackage{siunitx}                  % for the use of SI unite in mathmode

\usepackage{xcolor}                   % colours bro

\usepackage{upquote}                  % straight quotes in verbatim environments

\usepackage{unicode-math}             % allows unicode characters in mathmode

\usepackage[pdfa, unicode]{hyperref}  % hyperlinks and PDF metadata manipulation

\usepackage{tikz}                     % drawing

\usepackage[siunitx]{circuitikz}      % drawing circuits

\usepackage{pgfplots}                 % plotting

\usepackage{geometry}                 % to set the margins of the page

%==============================================================================%
%                             Set package options                              %
%==============================================================================%

%============================%
%          AMSMath           %
%============================%

\allowdisplaybreaks

%============================%
%          Hyperref          %
%============================%

\hypersetup{
    pdftitle={A minimal reaction-diffusion neural model generates C. elegans undulation},
    pdfauthor={Anshul Singhvi},
    colorlinks=true,
    linkcolor=Maroon,
    citecolor=Blue,
    urlcolor=Blue,
    breaklinks=true,
    pdfdisplaydoctitle = true
}

%============================%
%         Microtype          %
%============================%

\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts

%============================%
%     TikZ and PGFPlots      %
%============================%

\usetikzlibrary{
    arrows.meta,
    calc,
    decorations,
    decorations.pathreplacing,
    decorations.footprints,
    math,
    patterns,
    shadows,
    external
}

\tikzset{>=stealth}

\pgfplotsset{compat=1.16}

\usepgfplotslibrary{
    polar,
    colormaps,
    colorbrewer,
    groupplots,
    statistics
}

% This cycle list encodes the Wong colors, which are visually distinguishable.
% They also account for colorblind support, and as such are optimal for use in a paper.
\pgfplotscreateplotcyclelist{wong}{%
    color={rgb, 255 : red, 86  ; green, 180 ; blue, 233}, mark = *\\         % sky blue
    color={rgb, 255 : red, 230 ; green, 159 ; blue, 0},   mark = square*\\   % orange
    color={rgb, 255 : red, 0   ; green, 158 ; blue, 115}, mark = otimes*\\   % blueish green
    color={rgb, 255 : red, 240 ; green, 228 ; blue, 66},  mark = star\\      % yellow
    color={rgb, 255 : red, 0   ; green, 114 ; blue, 178}, mark = diamond*\\  % blue
    color={rgb, 255 : red, 213 ; green, 94  ; blue, 0},   mark = triangle*\\ % vermillion
    color={rgb, 255 : red, 204 ; green, 121 ; blue, 167}, mark = pentagon*\\ % reddish purple
}

\pgfplotsset{every axis legend/.append style={%
        cells={anchor=west}
    },
    cycle list name = wong,
}

%============================%
%          Geometry          %
%============================%

\geometry{
  a4paper,
  margin = 1.2in
}

%==============================================================================%
%                         Macros and document options                          %
%==============================================================================%

\setstretch{1} % line spacing of 1.25

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
% \setcounter{secnumdepth}{0}
%
% % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
%     \let\oldparagraph\paragraph
%     \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
%     \let\oldsubparagraph\subparagraph
%     \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi

\newcommand{\inputtikz}[1]{%
  \tikzsetnextfilename{#1}%
  \input{#1.tikz}%
}

%==============================================================================%
%                            Neuron diagram macros                             %
%==============================================================================%

\newcommand{\doublec}[2]{% double diffusion arrows
  \draw  [-Circle] ($(#1.north east)!0.7!(#1.north)$) -- ($(#2.south east)!0.7!(#2.south)$);
  \draw  [Circle-] ($(#1.north west)!0.7!(#1.north)$) -- ($(#2.south west)!0.7!(#2.south)$);
  }

\newcommand{\singlec}[2]{% single diffusion arrows
  \draw [-Latex] (#1.east) -- (#2.west);
  }

% Set the TikZ neuron style up, since it's used many times
\tikzset{
  neuron/.style={
  % The shape:
  circle,
  % The size:
  minimum size=6mm,
  % The border:
  very thick,
  draw=blue!50!black!50,
  % The filling:
  top color=white,
  bottom color=blue!50!black!20, % and something else at the bottom
  % Font
  font=\itshape,
  % padding around node
  outer sep=2mm
  }
}

### 2020-04-16 paper.tex
Add circuit figures

\documentclass[
    11pt,
]{article}

\usepackage{authblk}

% \usepackage{natbib}
% \setcitestyle{nature}

\usepackage[style=nature, natbib]{biblatex}

\addbibresource{References.bib}

\input{preamble.tex}

\tikzexternalize

\begin{document}
% \sffamily

%==============================================================================%
%                              Title and abstract                              %
%==============================================================================%

\title{A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation}

\author[1]{Anshul Singhvi}

\author[1,3]{Harold Hastings}

\author[2]{Jennifer Magnes}

\author[2]{Cheris Congo}

\author[2]{Miranda Hulsey-Vincent}

\author[1]{Rifah Tasnim}

\author[1]{Naol Negassa}

\affil[1]{Bard College at Simon's Rock}
\affil[2]{Vassar College}
\affil[3]{Hofstra University}

\date{\today}

\begin{abstract}
    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C. elegans} connectome has been completely mapped, and \emph{C. elegans} locomotion has been widely studied (c.f. http://www.wormbook.org \citet{corsi2015}). We describe a minimal reaction-diffusion model for the \emph{C. elegans} central pattern generator (CPG) \citet{xu2018,wen2012}. We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C. elegans} undulation (see \citet{magnes2012}), and thus locomotion. Compare the neuromechanical model of \citet{izquierdo2018}. We also investigate dynamics and stability of the model.
    % TODO: expand and inflate; fix grammar
\end{abstract}

\maketitle

\section{Introduction}\label{sec: intro}

The small (1 mm) nematode \emph{Caenorhabditis elegans} (\emph{C. elegans}) has become widely used as a model organism \citep{corsi2015}, and has been among the most widely studied biological models of neuronal development, locomotion and the central pattern generator \citep{katz2016}.
The C. elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied.
``When crawling on a solid surface, the nematode C. elegans moves forward by propagating sinusoidal dorso-ventral retrograde contraction waves. A uniform propagating wave leads to motion that undulates about a straight line.'' \citep{kim2011}.
A different type of locomotion, often called swimming, occurs when nematodes are submerged in a liquid medium. The nematodes “switch” between these two gaits, under the regulation of particular serotonergic and dopaminergic neurons.

% TODO:
% - decide whether to cite CPG
% - italicise C. elegans
The purpose of this paper to describe a minimal reaction-diffusion model for the \emph{C. elegans} central pattern generator (CPG) \citep{xu2018, wen2012}. We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) based on a skeleton model of the C. elegans CPG can reproduce key features of C. elegans undulation \citep{magnes2012} and thus locomotion.

In addition to simulating the CPG, we also implemented a modified version of the FitzHugh-Nagumo neuron, originally proposed by \citet{keener1983}, as an analog circuit.  This circuit solves the Keener differential equations, and we adjusted it to allow diffusive coupling between neurons.  We made a small network with these ``neuro-mimetic'' circuits, and showed that their behaviour replicates FitzHugh-Nagumo simulated behaviour.

\section{The model central pattern generator}

% TODO confirm the Xu reprint policy

A central pattern generator is a small neural circuit which generates and regulates the movement of complex organisms.  This structure is present in different forms in many animals, and it regulates many types of periodic motion.  \citet{xu2018} proposed an architecture for the CPG of \emph{C. elegans} which is described below in \fref{fig: xu_cpg}.

In more complex animals, like horses or humans, there is only one CPG; the dynamics of the CPG change depending on the gait of the animal \citep{collins1994}.  We show later that breaking the symmetry of the CPG model can lead to radical changes in behaviour.

\begin{figure}[h!]
    \label{fig: xu_cpg}
    \centering
    \includegraphics[width=9cm]{figures/xu_cpg/xu_cpg.png}
    \caption{Pirated from Xu.}
\end{figure}

The central pattern generator has two principal components.  First is the \textbf{head oscillator}. As described by \citet{gjorgjieva2014}, the head oscillator consists of two “head neurons” with mutually inhibitory coupling.  Oscillations are generated when this coupling destabilizes an excitable steady state.
% This is destablilzing to a stable limit cycle.  Mutual inhibition leads to a 180-deg out of phase oscillation - describe this in more detail.
% TODO experiment on a single head oscillator.
% TODO explain how coupling works

Second is the \textbf{descending pathway}, which consists of pairs of coupled, excitable, dorsal and ventral neurons.  These follow the body of the worm, and are linked to motor neurons and muscles.  The head oscillator drives the descending pathway, and the pathway is kept in sync by mutual inhibitory coupling between neurons.

One can think of the CPG as a driven, dissipative system.  An analogy to the driven, damped oscillator is particularly apt - in the CPG, the head oscillator drives the descending pathway.

While \textit{C. elegans} has twelve pairs of motor neurons, we have only used six pairs in our model.  \Fref{fig: cpg} is a depiction of our simplified model as a graph, wherein neurons are nodes, and the arrows between them symbolize connections.

\begin{figure}[h!]
    \label{fig: cpg}
    \centering
    \inputtikz{figures/cpg/cpg}
    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
\end{figure} % TODO: legend

\section{The FitzHugh-Nagumo Neuron}\label{sec: fhn}

In accord with the goal of this paper, we sought the simplest relevant neuronal model.  The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo models.

The FHN model consists of two dynamical variables; a fast activator variable $v$ corresponding to the (rescaled) membrane potential, and a slow inhibitor variable $w$ corresponding to a generalized gating variable.

\begin{equation} % reference HH model here as well
    \label{eq: fhn}
    \begin{aligned}
        dv &= f(v) + w - I_\mathrm{ext}\\
        dw &= ϵ(a - bv)\\
        f(v) &= \frac{v^3}{3} - v
    \end{aligned}
\end{equation}

% The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.  Nagumo's tunnel diode describes the same behaviour.  The point is that in the oscillatory regime the system is a relaxation oscillator, and that it has an excitable regime.

In this system, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v)$.  In our analog implementation, we use a piecewise linear approximation to the cubic, in order to simplify the circuit and avoid using expensive components.

Xu et al. used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline). Both the Morris-Lecar model and the Fitzhugh-Nagumo model have similar activator nullclines.

% TODO: remove Morris-Lecar
% remark that if the w and v nullclines come near each other, you see a critical slowdown.
% In Hodgkin-Huxley notation, $n$ is the potassium channel.  In the FHN formulation, this corresponds to the $w$ gate variable.
\begin{figure}[h!]
    \label{fig: nm nullclines}
    \centering
    \inputtikz{figures/neuron_dynamics/neuron_dynamics}
    % TODO: change legend to dv/dt=0, dw/dt=0
    % relabel ``real c. elegans'' to C. elegans (experimental data).
    % for publication: remove ticklabels, keep minor grid
    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, in the centre is the Morris-Lecar model, and to the right is the FitzHugh-Nagumo model.  These have been arranged in order of decreasing complexity.}
\end{figure} % TODO: legend

The original system was meant to model one neuron only.  We use diffusion to
model a synapse. A positive coefficient would simulate a gap junction or
an excitatory synapse; a negative coefficient would simulate inhibitory
coupling (\citet{collins1994}).

% TODO: there will be other examples...cf them

The equations, when modified for synaptic connections, look like this:

\begin{equation}
    \label{eq: fhnd}
    \begin{aligned}
        dv   &= f(v) + w - I_\mathrm{ext} + D(Δv)\\ % highlight D?
        dw   &= ϵ(a - bv)\\
        f(v) &= \frac{v^3}{3} - v
    \end{aligned}
\end{equation}

\begin{figure}[h!]
    \label{fig: fhn_dynamics}
    \centering
    \inputtikz{figures/fhn_dynamics/fhn_dynamics}
    % TODO describe this more.
    % Show a sample trajectory in each of these.
    % remove the ticklabels
    % condense into single figure
    % Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$.
    \caption{The nullclines of the FitzHugh-Nagumo neuron.  Nullclines are isoclines where the derivative of a variable is zero.  Here we show an oscillatory mode and an excitable one.  In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.  See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
\end{figure} % TODO: legend

\section{Simulation}

The simulation was performed in Python, using the standard SciPy ODE solvers. % TODO list solver here

\subsection{Methods}

See the appendix, or attached code, for how we simulated this motion.  It should probably also be published on Github - I could make a Jupyter notebook with it.

We realize the network shown in \Fref{fig: cpg} into a system of ODEs, and solve it.  The equations are integrated, giving a timeseries of neuronal potentials.  These are passed through filters to simulate muscular movement and the resistance of the medium.  We used Gaussian smoothing and B-splines for this purpose.

We generated a video by fixing the head of a worm to the origin, and re-normalizing the coordinates resulting from the filtering.

\subsection{Comparison to real worm}

Cite the paper which Jenny sent here.  It can be seen that our model closely approximates an unconstrained worm, specifically of the wild type.

While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos . It is not hard to see that a fully unconstrained worm might behave much like our model does.

\section{Analog implementation}

\citet{nagumo1962} proposed a circuit to simulate a FitzHugh-Nagumo neuron, shown in \Fref{fig: nagumo_ckt}.  It used a tunnel diode to achieve a cubic-like activation function, and an inductor to integrate.  However, this approach presents several complications.  Tunnel diodes are rare, and rather expensive; inductors cannot be used in proximity because of mutual inductance effects, and are quite large.

\begin{figure}[h!]
    \centering
    \inputtikz{figures/nagumo/nagumo}
    \caption{The original circuit proposed by \citet{nagumo1962}.  Note the use of inductors for integration, and the tunnel diode to supply a cubic-like V-I curve.  Our circuit, based off \citet{keener1983}, is arranged in the same layout, to make the similarities and differences more explicit.}
    \label{fig: nagumo_ckt}
\end{figure}

\citet{keener1983} proposed a modified Nagumo circuit which used operational amplifiers ("op-amps") to achieve nonlinearity and create a piecewise linear function.  He used an op-amp under saturation to create a piecewise linear approximation to the cubic, which is sufficient to drive the FHN oscillator.  He also used an op-amp integrator to simulate an inductor.

As a result of the piecewise linear approximation to the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.  However, in experiments this did not cause any change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.

Our modifications to Keener's proposed circuit are mainly concerned with diffusive coupling between neurons.  If each individual circuit is thought of as a single neuron, then we implemented diffusive coupling methods between those neurons.  We also found that you don't need separate power supplies, and you can get finer control by adjusting the bias voltage and input through a separate mechanism.

\begin{figure}[h!]
    \centering
    \inputtikz{figures/neuron_unit/neuron_unit}
    \caption{The circuit we created, based of \citet{keener1983}.  Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit looks more complex, in practice it is quite simple to implement.}
    \label{fig: nagumo_ckt}
\end{figure}

- Nagumo circuit, disadvantages

- Keener improved, op amps, why is that good - scalability, etc. Piecewise (N-shaped) linear approximation.

- Our modifications - diffusion, coupling mechanism.  Some mention of mathematics involved

- Figures: circuits, circuit nullclines,

\citet{nagumo1962} proposed a circuit which could simulate the system which FitzHugh proposed.  A depiction is included in \Fref{fig: nagumo_ckt}.

To compare the analog implementation with our simulated model, we will focus on the timeseries output of the neurons, and not on the end worm.  Include the relevant figure here - you can see clearly that the effect is the same.  There are some differences in the waveform because of the different activation function in the circuit (linear interpolation).

% \begin{figure}
%
% \end{figure}

\section{Conclusion}

Mention the bullet points from the presentation.  How could a system like this be used in applications?  End with some future paths.

Reference some connections to \citet{adamatzky2008} - the neural system as a computational system.  Also cite similarity between B-Z and FHN.

\section{References}

% \nocite{*}
% \bibliography{References}
\printbibliography[heading=none]
\end{document}

### 2020-04-16 paper.tex
Fix label conflict
Add blurb about coupling
Need to add the actual figures.  Will do when I have subfig "figured" out...

@@
 In our analog implementation, we use a piecewise linear approximation to the cubic, in order to simplify the circuit and avoid using expensive components.
+Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$
 
@@
 used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
-Both the Morris-Lecar model and the Fitzhugh-Nagumo model have similar activator nullclines.
+BothThe Fitzhugh-Nagumo model has similar activator nullclines.
 
@@
     % condense into single figure
-    % Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$.
+    % .
     \caption{The nullclines of the FitzHugh-Nagumo neuron.
@@
 
-The simulation was performed in Python, using the standard SciPy ODE solvers. % TODO list solver here
+The simulation was performed in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here
 
@@
 Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit looks more complex, in practice it is quite simple to implement.}
-    \label{fig: nagumo_ckt}
+    \label{fig: neuron_unit}
 \end{figure}
 
-- Nagumo circuit, disadvantages
+However, this is only one neuron.
+In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.
+These mechanisms are shown in \Fref{fig: coupling_ckt}.
+We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).
+The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.
 
-- Keener improved, op amps, why is that good - scalability, etc. Piecewise (N-shaped) linear approximation.
-
-- Our modifications - diffusion, coupling mechanism.  Some mention of mathematics involved
-
-- Figures: circuits, circuit nullclines,
-
-\citet{nagumo1962} proposed a circuit which could simulate the system which FitzHugh proposed.  A depiction is included in \Fref{fig: nagumo_ckt}.
+\subsection{Comparison of analog and simulation}
 

### 2020-04-29 paper.tex
Fix Jenny's name
Co-authored-by: Jenny Magnes <jemagnes@vassar.edu>
temporary changes for pgfplots
this really needs to be better.
Review changes

@@
 
-\author[2]{Jennifer Magnes}
+\author[2]{Jenny Magnes}
 
@@
 
+% TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.
 \section{The model central pattern generator}
@@
 % TODO confirm the Xu reprint policy
+% TODO show how the latest paper describes a small sequence of neurons forming coupled oscillators.
 
@@
     % for publication: remove ticklabels, keep minor grid
+    % Replace the figure with Xu's
+    % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
     \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, in the centre is the Morris-Lecar model, and to the right is the FitzHugh-Nagumo model.
@@
 
-The simulation was performed in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here
+We performed the simulations in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here
 
@@
 The equations are integrated, giving a timeseries of neuronal potentials.
-These are passed through filters to simulate muscular movement and the resistance of the medium.
+These were passed through filters to simulate muscular movement and the resistance of the medium.
 We used Gaussian smoothing and B-splines for this purpose.
@@
 
-While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos .
+While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos.
 It is not hard to see that a fully unconstrained worm might behave much like our model does.
+
+The worm generates sinusoidal oscillations
+
+% Closely related to the first I&B (2008).  Alternate and likely more realistic structure with a distributed CPG was proposed by new Izquierdo.
 
@@
 
-% \begin{figure}
-%
-% \end{figure}
+\begin{figure}[h!]
+    \centering
+    \pgfplotsset{}
+    \inputtikz{figures/anal_sim_comp/anal_sim_comp}
+    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).}
+    \label{fig: anal_sim_comp}
+\end{figure}
+
+% TODO: write up a section on the Beer paper and see how it relates to our CPG model.
 

### 2020-05-01 paper.tex
Review with Harold

@@
 We describe a minimal reaction-diffusion model for the \emph{C.
+elegans} which realizes the neuromechanical model of \citet{izquierdo2018}.
+This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C.
 elegans} central pattern generator (CPG) \citet{xu2018,wen2012}.
-We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
+(Olivares et al.
+*** likely more realistic model which relies on dorsal-ventral coupling) In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
 elegans} undulation (see \citet{magnes2012}), and thus locomotion.
-Compare the neuromechanical model of \citet{izquierdo2018}.
-We also investigate dynamics and stability of the model.
-    % TODO: expand and inflate; fix grammar
+Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
+    % TODO: expand and inflate; fix grammar, cite Olivares2019
 \end{abstract}
@@
 elegans}) has become widely used as a model organism \citep{corsi2015}, and has been among the most widely studied biological models of neuronal development, locomotion and the central pattern generator \citep{katz2016}.
-The C. elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied.
+The C.
+elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).
+There are a variety of neuronal models which generate the undulation,
 ``When crawling on a solid surface, the nematode C.
@@
 % - italicise C. elegans
-The purpose of this paper to describe a minimal reaction-diffusion model for the \emph{C.
+The purpose of this paper is to describe a minimal, biomimetic, reaction-diffusion model for the \emph{C.
 elegans} central pattern generator (CPG) \citep{xu2018, wen2012}.
@@
 % TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.
+
+Olivares et al *** recently created a more biologically relevant model for the CPG, which argues that the CPG is a network of connected oscillators.
+The role of this paper is to show a very minimal model, and our approach has been to create a small and computationally cheap model.
+
 \section{The model central pattern generator}
@@
 
-In more complex animals, like horses or humans, there is only one CPG; the dynamics of the CPG change depending on the gait of the animal \citep{collins1994}.
+In more complex animals, like horses or dogs, there is only one CPG; the dynamics of the CPG change depending on the gait of the animal \citep{collins1994}.
 We show later that breaking the symmetry of the CPG model can lead to radical changes in behaviour.
@@
 Oscillations are generated when this coupling destabilizes an excitable steady state.
-% This is destablilzing to a stable limit cycle.  Mutual inhibition leads to a 180-deg out of phase oscillation - describe this in more detail.
+
+In the terms of dynamical systems analysis, the oscillations destabilize to a stable limit cycle.
+The mutual inhibition and symmetry between neuron pairs leads to a phase lock of $180^\circ$.
+This provides out-of-phase stimuli which propagate through the descending pathway, with the inhibition between neuron pairs keeping the oscillations stable.
 % TODO experiment on a single head oscillator.
@@
 
-One can think of the CPG as a driven, dissipative system.  An analogy to the driven, damped oscillator is particularly apt - in the CPG, the head oscillator drives the descending pathway.
+% TODO do we need this?  
+% One can think of the CPG as a driven, dissipative system.  An analogy to the driven, damped oscillator is particularly apt - in the CPG, the head oscillator drives the descending pathway.
 
+% TODO expand.  Our model could have had more neurons, with a shorter phase lag between pairs.
 While \textit{C.
@@
 
-% The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.
+The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.
 Nagumo's tunnel diode describes the same behaviour.
-The point is that in the oscillatory regime the system is a relaxation oscillator, and that it has an excitable regime.
+The necessary feature is that in the oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
 
@@
 used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
-BothThe Fitzhugh-Nagumo model has similar activator nullclines.
+The Fitzhugh-Nagumo model has similar activator nullclines.
 
@@
 
-The original system was meant to model one neuron only.  We use diffusion to
-model a synapse. A positive coefficient would simulate a gap junction or
+% TODO: see if anyone else used diffusion to couple neurons
+The original system was meant to model one neuron only.  Following ***, we used 
+generalized diffusion coupling between FHN neurons to mimic synapses. 
+A positive coefficient would simulate a gap junction, or
 an excitatory synapse; a negative coefficient would simulate inhibitory
@@
 
-See the appendix, or attached code, for how we simulated this motion.  It should probably also be published on Github - I could make a Jupyter notebook with it.
+See the appendix, or attached code, for how we simulated this motion.  It will be published on Github with embedded plots, so people can see it.
 
@@
 We used Gaussian smoothing and B-splines for this purpose.
+% TODO: reference for muscle response time
 
@@
 % TODO: write up a section on the Beer paper and see how it relates to our CPG model.
+% Perhaps a discussion about the "scientific lineage" of our model, and the Olivares et al model.  
+% Paraphrase their description.
 
@@
 Mention the bullet points from the presentation.  How could a system like this be used in applications?  End with some future paths.
+
+% The particular model doesn't really matter; if you have the right topology, you can generate the behaviour.
+% Reservoir computing and our neurons.  Speculate that different circuits of FHN neurons might be suitable dynamical reservoirs.  However, a CPG has a range of comparatively simple dynamics.
+% cite Sanchez-Sinencio, Spano on circuits.  Theirs emphasize accuracy whereas ours emphasizes speed and minimal cost.
 

### 2020-05-02 paper.tex
Small changes to paper, references, etc

@@
 elegans} central pattern generator (CPG) \citet{xu2018,wen2012}.
-(Olivares et al.
-*** likely more realistic model which relies on dorsal-ventral coupling) In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
+\citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG.
+In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
 elegans} undulation (see \citet{magnes2012}), and thus locomotion.
@@
     \centering
-    \inputtikz{figures/fhn_dynamics/fhn_dynamics}
+    \includegraphics{figures/fhn_dynamics/fhn_dynamics.pdf}
     % TODO describe this more.

### 2020-05-18 paper.tex
Updates from Overleaf

--- 2020-05-01 paper.tex
@@
 
-\section{The FitzHugh-Nagumo Neuron}\label{sec: fhn}
+\section{The FitzHugh-Nagumo Neuronal Model}\label{sec: fhn}
 
 In accord with the goal of this paper, we sought the simplest relevant neuronal model.
-The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo models.
+The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo (FHN) models.
 
@@
 \end{equation}
-
-The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.
-Nagumo's tunnel diode describes the same behaviour.
-The necessary feature is that in the oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
 
@@
 \citet{nagumo1962} proposed a circuit to simulate a FitzHugh-Nagumo neuron, shown in \Fref{fig: nagumo_ckt}.
-It used a tunnel diode to achieve a cubic-like activation function, and an inductor to integrate.
+It used a tunnel diode to achieve a cubic-like activation function, and an inductor to differentiate the K current.
 However, this approach presents several complications.
@@
     \caption{The original circuit proposed by \citet{nagumo1962}.
-Note the use of inductors for integration, and the tunnel diode to supply a cubic-like V-I curve.
+Note the use of inductors for differentiation, and the tunnel diode to supply a cubic-like V-I curve.
 Our circuit, based off \citet{keener1983}, is arranged in the same layout, to make the similarities and differences more explicit.}
@@
 
-\citet{keener1983} proposed a modified Nagumo circuit which used operational amplifiers ("op-amps") to achieve nonlinearity and create a piecewise linear function.
-He used an op-amp under saturation to create a piecewise linear approximation to the cubic, which is sufficient to drive the FHN oscillator.
-He also used an op-amp integrator to simulate an inductor.
+The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.
+Nagumo's tunnel diode describes the same behaviour.
+The necessary feature is that in the oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
+
+\citet{keener1983} proposed a modified Nagumo circuit which used the saturation properties of operational amplifiers ("op-amps") to achieve cubic-like non-linearity in the FHN  model.He also used an op-amp and a capacitor to simulate the inductor in the original Nagumo circuit.
 
 As a result of the piecewise linear approximation to the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.
-However, in experiments this did not cause any change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.
+However, in experiments this did not cause a significant change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.
 

### 2020-06-04 paper.tex
work

@@
 We describe a minimal reaction-diffusion model for the \emph{C.
-elegans} which realizes the neuromechanical model of \citet{izquierdo2018}.
+elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}.
 This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C.
@@
 elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).
-There are a variety of neuronal models which generate the undulation,
+There are a variety of neuronal models which can generate such undulation,
 ``When crawling on a solid surface, the nematode C.
@@
 In more complex animals, like horses or dogs, there is only one CPG; the dynamics of the CPG change depending on the gait of the animal \citep{collins1994}.
+The mode of locomotion depends on the sequencec in which the neurons fire, but the network's topology remains the same.
 We show later that breaking the symmetry of the CPG model can lead to radical changes in behaviour.
@@
         dv &= f(v) + w - I_\mathrm{ext}\\
-        dw &= ϵ(a - bv)\\
+        dw &= \epsilon (a - bv)\\
         f(v) &= \frac{v^3}{3} - v
@@
 These have been arranged in order of decreasing complexity.}
-\end{figure} % TODO: legend
+\end{figure}
 
@@
     \begin{aligned}
-        dv   &= f(v) + w - I_\mathrm{ext} + D(Δv)\\ % highlight D?
+        dv   &= f(v) + w - I_\mathrm{ext} + \color{green}{D(Δv)}\\
         dw   &= ϵ(a - bv)\\
@@
 \end{equation}
+
+where $\Delta v$ is the difference in voltage between the driving and driven neurons, essentially $\Delta v = v_{driven} - v_{driving}$.
 
@@
 
-The sodium channel has a negative resistance regime, wherein the current decreases as the voltage increases.
-Nagumo's tunnel diode describes the same behaviour.
+% The circuit in \Fref{fig: nagumo_ckt} is an analog solver for the FitzHugh-Nagumo equations.  Namely, the
+
+The sodium channel in the FitzHugh-Nagumo equations has a negative resistance regime, wherein the current decreases as the voltage increases.
+Nagumo's tunnel diode exhibits this behaviour, but it may be replaced by any device with a similarly nonlinear V-I curve.
 The necessary feature is that in the oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
 
-\citet{keener1983} proposed a modified Nagumo circuit which used the saturation properties of operational amplifiers ("op-amps") to achieve cubic-like non-linearity in the FHN  model.He also used an op-amp and a capacitor to simulate the inductor in the original Nagumo circuit.
+\citet{keener1983} proposed a modified Nagumo circuit which used the saturation properties of operational amplifiers ("op-amps") to achieve cubic-like non-linearity in the FHN model.
+He also used an op-amp and a capacitor to simulate the inductor in the original Nagumo circuit.
 
@@
 The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.
+\newsavebox{\tempbox}
+\begin{figure}
+    \centering
+    \inputtikz{figures/coupling/coupling}
+    \caption{Coupling methods}
+    \label{fig: coupling}
+\end{figure}
 
@@
 
+We have shown that the undulatory motion of \emph{C.
+elegans} can be simulated using a structured central pattern generator, and simple, biomimetic neurons.
+This system is computationally cheap, and translates to a simple analog circuit.
+
+Our model of the nematode is surprisingly similar to real unconstrained motion.
+
+% Can we use this to explore how mutations effect motion, and mechanisms behind differences in phenotypes.
 % The particular model doesn't really matter; if you have the right topology, you can generate the behaviour.

### 2020-06-07 paper.tex
work
more work

@@
 
-% TODO confirm the Xu reprint policy
 % TODO show how the latest paper describes a small sequence of neurons forming coupled oscillators.
@@
 In more complex animals, like horses or dogs, there is only one CPG; the dynamics of the CPG change depending on the gait of the animal \citep{collins1994}.
-The mode of locomotion depends on the sequencec in which the neurons fire, but the network's topology remains the same.
+The mode of locomotion depends on the sequence in which the neurons fire, but the network's topology remains the same.
 We show later that breaking the symmetry of the CPG model can lead to radical changes in behaviour.
@@
     \includegraphics[width=9cm]{figures/xu_cpg/xu_cpg.png}
-    \caption{Pirated from Xu.}
+    \caption{The central pattern generator proposed by \citet{xu2018}.  Note the structure of the neurons, especially the head oscillator driving the descending pathway.}
 \end{figure}
@@
 
-\begin{equation} % reference HH model here as well
+\begin{equation}
     \label{eq: fhn}
@@
 \end{equation}
+
+The parameter $I_\mathrm{ext}$ is an external driving current, and can also be used to increase excitability.
+In the analog implementation, this is an integral component of tuning the neuron's frequency response.
 
@@
     \centering
-    \inputtikz{figures/neuron_dynamics/neuron_dynamics}
-    % TODO: change legend to dv/dt=0, dw/dt=0
-    % relabel ``real c. elegans'' to C. elegans (experimental data).
-    % for publication: remove ticklabels, keep minor grid
-    % Replace the figure with Xu's
+    \includegraphics{figures/neuron_dynamics/neuron_dynamics.pdf}
     % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
@@
     \includegraphics{figures/fhn_dynamics/fhn_dynamics.pdf}
-    % TODO describe this more.
-    % Show a sample trajectory in each of these.
-    % remove the ticklabels
-    % condense into single figure
-    % .
     \caption{The nullclines of the FitzHugh-Nagumo neuron.
@@
     \pgfplotsset{}
-    \inputtikz{figures/anal_sim_comp/anal_sim_comp}
+    % \inputtikz{figures/anal_sim_comp/anal_sim_comp}
+    \includegraphics{figures/anal_sim_comp/anal_sim_comp}
     \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).}
@@
 Our model of the nematode is surprisingly similar to real unconstrained motion.
+While most measurements of \emph{C.
+elegans} are taken on horizontal agar sheets, observations made in clear, water-filled cuvettes where the worm floats freely seem to resemble our simulated worm more.
 
-% Can we use this to explore how mutations effect motion, and mechanisms behind differences in phenotypes.
+Given the flexibility of the model, by introducing defects and asymmetries into the topology, we can study how mutations affect the nematode's motion, as well as the structures underlying differences in phenotypes.
+
 % The particular model doesn't really matter; if you have the right topology, you can generate the behaviour.

### 2020-12-25 paper.tex
Updates from Overleaf

--- 2020-06-04 paper.tex
@@
 \begin{abstract}
+% Note: this is project https://www.overleaf.com/project/5e984f87a777200001dcff7e
+
     The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C.
@@
 elegans} locomotion has been widely studied (c.f.
-http://www.wormbook.org \citet{corsi2015}).
+http://www.wormbook.org \citet{corsi2015}) *** also other ref ***.
 We describe a minimal reaction-diffusion model for the \emph{C.
@@
 Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
-    % TODO: expand and inflate; fix grammar, cite Olivares2019
+    \citet{olivares2018potential}
+    \citet{olivares2019}
+    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}
+
 \end{abstract}
@@
 Xu et al.
-used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
+described a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
 The Fitzhugh-Nagumo model has similar activator nullclines.

### 2020-12-25 paper.tex
Some minor changes to phrasing

--- 2020-06-07 paper.tex
@@
 
+There are many other models for the CPG; for example, a 2019 preprint by \cite{olivares2019} proposes a distributed network of oscillating systems, instead of a structured chain like our proposed CPG.
+The point of this paper is to create a minimal working model, though, and not to strive for full realism.
+
 % TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.
@@
 This provides out-of-phase stimuli which propagate through the descending pathway, with the inhibition between neuron pairs keeping the oscillations stable.
-% TODO experiment on a single head oscillator.
-% TODO explain how coupling works
 
@@
 
-% TODO do we need this?
-% One can think of the CPG as a driven, dissipative system.  An analogy to the driven, damped oscillator is particularly apt - in the CPG, the head oscillator drives the descending pathway.
-
 % TODO expand.  Our model could have had more neurons, with a shorter phase lag between pairs.
@@
 elegans} has twelve pairs of motor neurons, we have only used six pairs in our model.
+An equivalent result could be obtained with more neurons, by increasing the coefficient of diffusion along the pathway, causing a shorter phase lag between neuron pairs.
 \Fref{fig: cpg} is a depiction of our simplified model as a graph, wherein neurons are nodes, and the arrows between them symbolize connections.
@@
 
-% TODO: remove Morris-Lecar
 % remark that if the w and v nullclines come near each other, you see a critical slowdown.
@@
 
+\subsection{Generating undulation from neuron potential}
+
+The CPG network which we created is of the same form as the 2-D musculature of our simulated worm.
+Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.​  We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.
+Through Gaussian smoothing, the movement is heavily dependent on the current state of the neuron but also dependent somewhat on the history.
+​
+
+Much like \citet{izquierdo2018} did, we take a segment-based approach to the worm model.
+Pairs of muscles on either side determine the overall angular displacement per segment.​  The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​  We use a cubic spline interpolation to smoothen the worm body.
+
+Each neuron is assumed to be connected to a muscle; when it fires, it should cause that muscle to contract.​
+Pairs of neurons on either side determine the overall angular displacement per segment.​
+Gaussian smoothing and a cubic spline are used to mimic muscle movement and medium resistance.​
+The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​
+
+In this model, muscles can be seen as “leaky integrators” (Boyle et al. 2012) – the movement is heavily dependent on the current state of the neuron but is also dependent somewhat on the history.
+
 \subsection{Comparison to real worm}
@@
 
-The worm generates sinusoidal oscillations
+The worm undulates in a sinusoidal manner, both in simulation and reality.
 
@@
 
+\subsection{}
 % TODO: write up a section on the Beer paper and see how it relates to our CPG model.
@@
 \section{Conclusion}
-
-Mention the bullet points from the presentation.  How could a system like this be used in applications?  End with some future paths.
 

### 2020-12-25 paper.tex
Fix references

@@
 elegans} locomotion has been widely studied (c.f.
-http://www.wormbook.org \citet{corsi2015}) *** also other ref ***.
+http://www.wormbook.org \citet{corsi2015}).
 We describe a minimal reaction-diffusion model for the \emph{C.
@@
 Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
-    \citet{olivares2018potential}
     \citet{olivares2019}
@@
 
-% TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.
-
-Olivares et al *** recently created a more biologically relevant model for the CPG, which argues that the CPG is a network of connected oscillators.
+\citet{olivares2019} recently created a more biologically relevant model for the CPG, which argues that the CPG is a network of connected, self-oscillating systems.
 The role of this paper is to show a very minimal model, and our approach has been to create a small and computationally cheap model.
@@
 \begin{figure}[h!]
-    \label{fig: cpg}
     \centering
     \inputtikz{figures/cpg/cpg}
+    \label{fig: cpg}
     \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
@@
 
-\subsection{}
+\subsection{Relevance of \citet{izquierdo2018} to our model}
 % TODO: write up a section on the Beer paper and see how it relates to our CPG model.
@@
 % Paraphrase their description.
+
+The \citet{izquierdo2018} model is based on physical realities, and was generated using an evolutionary modelling process to find the structure of the descending neural network which controls muscular motion.
+As a result, the model, while realistic, is complex, and differs from ours in several places.
+First, the model is not a simple descending linked chain but a complex graphlike structure with repeating, complex self-oscillatory systems of neurons.
+
+Our goal in modelling \emph{C.
+elegans} is not to produce a very physically accurate model, but rather to replicate those behaviours which are essential - and only those - to the movement of the nematode.
+As such, we have the liberty of producing a simpler and more easily quantifiable model.
 

### 2020-12-25 paper.tex
Harold's edits to abstract

@@
 
-    The small (1 mm) nematode \emph{Caenorhabditis elegans} has become widely used as a model organism; in particular the \emph{C.
+    The small (1 mm) nematode \emph{Caenorhabditis elegans} \cite{corsi2015} has become widely used as a model organism; in particular the \emph{C.
 elegans} connectome has been completely mapped, and \emph{C.
-elegans} locomotion has been widely studied (c.f.
-http://www.wormbook.org \citet{corsi2015}).
-We describe a minimal reaction-diffusion model for the \emph{C.
-elegans}, which results in similar behaviour to the neuromechanical model of \citet{izquierdo2018}.
-This  may be considered as a simple model for Xu et al.'s "descending pathway" description of the \emph{C.
+elegans} locomotion has been widely studied (\citet{corsi2015}).
+We describe a minimal reaction-diffusion model for the locomotion of \emph{C.
+elegans}, using as a framework a simplified version of Xu et al.'s "descending pathway" description of the \emph{C.
 elegans} central pattern generator (CPG) \citet{xu2018,wen2012}.
-\citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG.
+Finally, we realize a model of the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
+    We note that \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG.
 In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
 elegans} undulation (see \citet{magnes2012}), and thus locomotion.
-Finally, we recreate the required oscillations and coupling with a network of coupled \citet{keener1983} analog neurons.
-    \citet{olivares2019}
-    % TODO: expand and inflate; fix grammar, cite Olivares2019, \citet @article{olivares2018potential}
-
 \end{abstract}
@@
 \begin{figure}[h!]
+    \ContinuedFloat
     \centering
@@
     \centering
-    \includegraphics{figures/fhn_dynamics/fhn_dynamics.pdf}
+    \includegraphics[height=5cm]{figures/fhn_dynamics/fhn_dynamics.pdf}
     \caption{The nullclines of the FitzHugh-Nagumo neuron.

### 2020-12-25 paper.tex
Harold's edits to intro

@@
 The small (1 mm) nematode \emph{Caenorhabditis elegans} (\emph{C.
-elegans}) has become widely used as a model organism \citep{corsi2015}, and has been among the most widely studied biological models of neuronal development, locomotion and the central pattern generator \citep{katz2016}.
+elegans}) has become widely used as a model organism (cf.
+http://www.wormbook.org \cite{corsi2015}), and has been among the most widely studied biological models of neuronal development and locomotion \citep{katz2016, corsi2015}.
 The C.
@@
 
-In addition to simulating the CPG, we also implemented a modified version of the FitzHugh-Nagumo neuron, originally proposed by \citet{keener1983}, as an analog circuit.
+Finally, we describe an analog electronic implementation of our model through solving a modified version of the FitzHugh-Nagumo neuron \cite{fitzhugh1955}, based upon an analog circuit originally proposed by \citet{keener1983}.
 This circuit solves the Keener differential equations, and we adjusted it to allow diffusive coupling between neurons.
@@
 
-There are many other models for the CPG; for example, a 2019 preprint by \cite{olivares2019} proposes a distributed network of oscillating systems, instead of a structured chain like our proposed CPG.
+There are many other models for the CPG; for example, a 2019 preprint by \cite{olivares2019} proposes a distributed network of self-oscillating systems of neurons, instead of a structured chain like our proposed CPG.
 The point of this paper is to create a minimal working model, though, and not to strive for full realism.

### 2020-12-25 paper.tex
More changes from Harold

@@
     \begin{aligned}
-        dv &= f(v) + w - I_\mathrm{ext}\\
-        dw &= \epsilon (a - bv)\\
+        \frac{dv}{dt} &= f(v) + w - I_\mathrm{ext}\\
+        \frac{dw}{dt} &= \epsilon (a - bv)\\
         f(v) &= \frac{v^3}{3} - v
@@
 In this system, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v)$.
-In our analog implementation, we use a piecewise linear approximation to the cubic, in order to simplify the circuit and avoid using expensive components.
-Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$
+For example, the cubic-like I-V curve of the tunnel diode used by Nagumo \cite{nagumo1962}, or even the piecewise linear approximation of the Keener circuit \cite{keener1983} which we use, would fit this criterion.
 
-Xu et al.
-described a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
-The Fitzhugh-Nagumo model has similar activator nullclines.
+In our analog implementation, we use a piecewise linear approximation to the cubic, the same as the Keener circuit \cite{keener1983}, in order to simplify the circuit and avoid using expensive components.
+Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$.
+
+\citet{xu2018} described a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
+The original Fitzhugh-Nagumo model has similar activator nullclines.
 
@@
     % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
-    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, in the centre is the Morris-Lecar model, and to the right is the FitzHugh-Nagumo model.
-These have been arranged in order of decreasing complexity.}
+    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, and to the right is the FitzHugh-Nagumo model.}
 \end{figure}
@@
     \begin{aligned}
-        dv   &= f(v) + w - I_\mathrm{ext} + \color{green}{D(Δv)}\\
-        dw   &= ϵ(a - bv)\\
+        \frac{dv}{dt}   &= f(v) + w - I_\mathrm{ext} + \color{green}{D(Δv)}\\
+        \frac{dw}{dt}   &= ϵ(a - bv)\\
         f(v) &= \frac{v^3}{3} - v
@@
     \centering
-    \includegraphics[height=5cm]{figures/fhn_dynamics/fhn_dynamics.pdf}
+    \includegraphics[height=8cm]{figures/fhn_dynamics/fhn_dynamics.pdf}
     \caption{The nullclines of the FitzHugh-Nagumo neuron.

### 2020-12-25 paper.tex
Updates from Overleaf

@@
     % \inputtikz{figures/anal_sim_comp/anal_sim_comp}
-    \includegraphics{figures/anal_sim_comp/anal_sim_comp}
-    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).}
+    \includegraphics[height=9cm]{figures/anal_sim_comp/anal_sim_comp.pdf}
+    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).
+(a) is the nullcline for the FitzHugh-Nagumo (simulated) equations, (b) is the "head oscillator" simulated (two neurons which mutually inhibit each other), (c) is the "descending pathway" simulated (one neuron driving another).
+(d) is the nullcline for the analog circuit - a piecewise linear approximation to the cubic, (e) is the analog version of the head oscillator, and (f) is the analog version of the descending pathway.}
     \label{fig: anal_sim_comp}

### 2020-12-25 paper.tex
Some changes made to captions, fixes, etc

@@
 \author[2]{Miranda Hulsey-Vincent}
+
+\author[2]{Susannah Zhang}
 
@@
 
-% TODO:
-% - decide whether to cite CPG
-% - italicise C. elegans
 The purpose of this paper is to describe a minimal, biomimetic, reaction-diffusion model for the \emph{C.
@@
 \begin{figure}[h!]
-    \label{fig: xu_cpg}
     \centering
@@
     \caption{The central pattern generator proposed by \citet{xu2018}.  Note the structure of the neurons, especially the head oscillator driving the descending pathway.}
+    \label{fig: xu_cpg}
 \end{figure}
@@
     \inputtikz{figures/cpg/cpg}
+    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
     \label{fig: cpg}
-    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
 \end{figure} % TODO: legend
@@
 
+Essentially, the way the code works is that the main function calculates the left-hand side of the system of differential equations which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.
+This is then run through an ODE solver which solves the trajectory of the system given some initial conditions (for example, if the neuron does not initially fire, for example, the system may remain in a steady state and not oscillate).
+
 \subsection{Methods}
@@
 The CPG network which we created is of the same form as the 2-D musculature of our simulated worm.
-Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.​  We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.
+Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.
+We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.
 Through Gaussian smoothing, the movement is heavily dependent on the current state of the neuron but also dependent somewhat on the history.
-​
 
 Much like \citet{izquierdo2018} did, we take a segment-based approach to the worm model.
-Pairs of muscles on either side determine the overall angular displacement per segment.​  The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​  We use a cubic spline interpolation to smoothen the worm body.
+Pairs of muscles on either side determine the overall angular displacement per segment.
+The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.
+We use a cubic spline interpolation to smoothen the worm body.
 
-Each neuron is assumed to be connected to a muscle; when it fires, it should cause that muscle to contract.​
-Pairs of neurons on either side determine the overall angular displacement per segment.​
-Gaussian smoothing and a cubic spline are used to mimic muscle movement and medium resistance.​
-The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.​
+Each neuron is assumed to be connected to a muscle; when it fires, it should cause that muscle to contract.
+Pairs of neurons on either side determine the overall angular displacement per segment.
+Gaussian smoothing and a cubic spline are used to mimic muscle movement and medium resistance.
+The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.
 
@@
 
-% The circuit in \Fref{fig: nagumo_ckt} is an analog solver for the FitzHugh-Nagumo equations.  Namely, the
-
 The sodium channel in the FitzHugh-Nagumo equations has a negative resistance regime, wherein the current decreases as the voltage increases.
@@
 In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.
-These mechanisms are shown in \Fref{fig: coupling_ckt}.
+These mechanisms are shown in \Fref{fig: coupling}.
 We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).

### 2020-12-26 paper.tex
Add worm-neuron dashboard
Updates from Overleaf
Changes by Jenny

@@
     We note that \citet{olivares2019} present a likely more realistic model which relies on small networks of neurons, and presents a distributed model of the CPG.
-In particular, we use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
+We use the simpler simulation to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) can generate key features of \emph{C.
 elegans} undulation (see \citet{magnes2012}), and thus locomotion.
@@
 The small (1 mm) nematode \emph{Caenorhabditis elegans} (\emph{C.
-elegans}) has become widely used as a model organism (cf.
-http://www.wormbook.org \cite{corsi2015}), and has been among the most widely studied biological models of neuronal development and locomotion \citep{katz2016, corsi2015}.
-The C.
-elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).
+elegans}) has become a widely used model organism (cf.
+http://www.wormbook.org \cite{corsi2015}), and has been among the most studied biological models of neuronal development and locomotion \citep{katz2016, corsi2015}.
+The \emph{C.
+elegans} connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).
 There are a variety of neuronal models which can generate such undulation,
@@
 
+% TODO:
+% - discuss dynamics of omega turn (central muscles contract in one direction, 
+%   extremities in another
+% -
+
 \subsection{Comparison to real worm}
@@
 The worm undulates in a sinusoidal manner, both in simulation and reality.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[height=13cm]{figures/worm_neuron_dash/worm_neuron_dash.pdf}
+    \caption{TODO}
+    \label{fig: worm_neuron_dash}
+\end{figure}
 

### 2020-12-26 paper.tex
add caption for worm neuron dash

@@
     \includegraphics[height=13cm]{figures/worm_neuron_dash/worm_neuron_dash.pdf}
-    \caption{TODO}
+    \caption{A "dashboard view" representing the neuron and worm.
+(a) shows the potentials of the ventral neurons, coloured by number running down the worm.
+(b) shows "images" of the simulated worm at different timepoints.
+The worm was simulated by running the neuron potentials through a Gaussian filter to simulate muscle dampening, then taking the amplitude as an angular displacement, representing contraction or relaxation.
+(c) shows images of a real \emph{C.
+elegans} in a cuvette, taken via shadow imaging.}
     \label{fig: worm_neuron_dash}

### 2020-12-27 paper.tex
Updates from Overleaf

@@
 The \emph{C.
-elegans} connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).
+elegans} connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015, gjorgjieva2014, }).
 There are a variety of neuronal models which can generate such undulation,
@@
 A uniform propagating wave leads to motion that undulates about a straight line.'' \citep{kim2011}.
-A different type of locomotion, often called swimming, occurs when nematodes are submerged in a liquid medium.
-The nematodes “switch” between these two gaits, under the regulation of particular serotonergic and dopaminergic neurons.
+A different type of locomotion, often called swimming, occurs when nematodes are submerged in a liquid medium. The nematodes “switch” between these two gaits, by changing the dynamics of the CPG.
 
@@
 elegans} central pattern generator (CPG) \citep{xu2018, wen2012}.
-We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) based on a skeleton model of the C.
-elegans CPG can reproduce key features of C.
-elegans undulation \citep{magnes2012} and thus locomotion.
+We use simulation methods to show that a small network of \citet{fitzhugh1955}-\citet{nagumo1962} neurons (one of the simplest neuronal models) based on a skeleton model of the \emph{C.
+elegans} CPG can reproduce key features of \emph{C.
+elegans} undulation \citep{magnes2012} and thus locomotion.
 
@@
 This circuit solves the Keener differential equations, and we adjusted it to allow diffusive coupling between neurons.
-We made a small network with these ``neuro-mimetic'' circuits, and showed that their behaviour replicates FitzHugh-Nagumo simulated behaviour.
+We constructed a small network with these ``neuro-mimetic'' circuits, and showed that their behaviour replicates FitzHugh-Nagumo simulated behaviour.
 
@@
 The point of this paper is to create a minimal working model, though, and not to strive for full realism.
+Our CPG model can be interpreted as having a graph-like structure, and it is easy to manipulate the "weights" of the edges (connections between neurons) of this "graph" to study defects or other changes in the CPG in an efficient, reproducible and explainable way.
 
@@
 \begin{figure}[h!]
+    % begin a continued float; see 
+    % https://tex.stackexchange.com/questions/118192/figure-subnumbering-1a
+    \ContinuedFloat* 
     \centering
@@
 
-The central pattern generator has two principal components.
+The simple model \emph{C.
+elegans} central pattern generator which is used here has two principal components.
 First is the \textbf{head oscillator}.
@@
 % TODO expand.  Our model could have had more neurons, with a shorter phase lag between pairs.
-While \textit{C.
+Although \emph{C.
 elegans} has twelve pairs of motor neurons, we have only used six pairs in our model.
@@
 \begin{figure}[h!]
+    % continue the previous continued float
     \ContinuedFloat
@@
     \inputtikz{figures/cpg/cpg}
-    \caption{Our simplified central pattern generator model.  Descending coupling (shows inhibitory connections, and potential flows through gap junctions, not necessarily symmetric)}
+    \caption{Our simplified central pattern generator model, based upon the descending pathway of Xu.
+The model includes inhibitory connections between corresponding dorsal and ventral neurons (denoted by subscripts $d$ and $v$, respectively) and a descending pathway of gap junctions.}
     \label{fig: cpg}
@@
 
-In accord with the goal of this paper, we sought the simplest relevant neuronal model.
+As described above, we sought the simplest relevant neuronal model.
 The classical Hodgkin-Huxley\cite{hodgkin1952} model of squid neurons has led to a variety of simpler conduction models, including the Morris-Lecar\cite{morris1981} and Fitzhugh-Nagumo (FHN) models.
@@
     \begin{aligned}
-        \frac{dv}{dt} &= f(v) + w - I_\mathrm{ext}\\
-        \frac{dw}{dt} &= \epsilon (a - bv)\\
+        \frac{dv}{dt} &= f(v) + w + I_\mathrm{ext}\\
+        \frac{dw}{dt} &= \varepsilon(v - \gamma w + \alpha )\\
         f(v) &= \frac{v^3}{3} - v
@@
 
-The parameter $I_\mathrm{ext}$ is an external driving current, and can also be used to increase excitability.
-In the analog implementation, this is an integral component of tuning the neuron's frequency response.
+The parameter $I_\mathrm{ext}$ is an external driving current, and is used here to model the effect of gap junctions and synapses upon membrane potential.
+The parameter $\alpha$ determines the vertical position of the $w$-nullcline and thus controls excitability.
+Action potentials can also be generated by a current injection corresponding to $I_\mathrm{ext}$.
+Finally, the parameter $\varepsilon$ determines ratio between the time scales of the fast activator variable $v$ and the slow inhibitor variable $w$; $\gamma$ limits the growth of $w$.
 
-In this system, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v)$.
-For example, the cubic-like I-V curve of the tunnel diode used by Nagumo \cite{nagumo1962}, or even the piecewise linear approximation of the Keener circuit \cite{keener1983} which we use, would fit this criterion.
-
-In our analog implementation, we use a piecewise linear approximation to the cubic, the same as the Keener circuit \cite{keener1983}, in order to simplify the circuit and avoid using expensive components.
-Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$.
+In addition, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v) = \frac{v^3}{3} - v$.
+For example, $f(v)$ could be replaced by the cubic-like I-V curve of the tunnel diode in the \citet{nagumo1962} circuit, or even the piecewise linear approximation generated in the \citet{keener1983} circuit used in our implementation.
 
 \citet{xu2018} described a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline).
-The original Fitzhugh-Nagumo model has similar activator nullclines.
+The \citet{xu2018} neuronal model can thus be interpreted as a Fitzhugh-Nagumo type model neuron.
 
@@
     % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
-    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, and to the right is the FitzHugh-Nagumo model.}
+    \caption{Dynamics of \textit{C. elegans} neurons following Xu \textit{et al.} \cite{xu2018} (left )and Fitzhugh-Nagumo neurons \cite{fitzhugh1955, nagumo1962} (right).}
 \end{figure}
@@
 % TODO: see if anyone else used diffusion to couple neurons
-The original system was meant to model one neuron only.  Following ***, we used
-generalized diffusion coupling between FHN neurons to mimic synapses.
-A positive coefficient would simulate a gap junction, or
-an excitatory synapse; a negative coefficient would simulate inhibitory
-coupling (\citet{collins1994}).
+ Following *** references are Collins and Richmond which you have and Yanagita T, Ichinomiya T, Oyama Y.
+Pair of excitable Fitzhugh-Nagumo elements: Synchronization, multistability, and chaos.
+Physical Review E.
+2005 Nov 28;72(5):056218.
+, we now use
+generalized diffusion coupling between FHN neurons to model gap junctions and synapses.
+The effect of gap junctions and synapses upon the membrane potential is modeled by replacing the external current $I_\mathrm{ext}$ of the system, by a generalized diffusion term $D \max(Δv,0)$.
+A positive diffusion coefficient $D$ is used to simulate a gap junction, or an excitatory synapse and a negative coefficient to simulate an inhibitory synapse (\citet{collins1994}).
 
@@
 
-The equations, when modified for synaptic connections, look like this:
+This yields the the system of (modified) FitzHugh-Nagumo equations:
 
@@
     \begin{aligned}
-        \frac{dv}{dt}   &= f(v) + w - I_\mathrm{ext} + \color{green}{D(Δv)}\\
+        \frac{dv}{dt}   &= f(v) + w  + \color{green}{D(Δv)}\\
         \frac{dw}{dt}   &= ϵ(a - bv)\\
@@
 In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.
-See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
+See \citet{parsons2018} for a detailed explanation of the dynamics of oscillatory biological systems.}
 \end{figure} % TODO: legend
@@
 
-Essentially, the way the code works is that the main function calculates the left-hand side of the system of differential equations which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.
-This is then run through an ODE solver which solves the trajectory of the system given some initial conditions (for example, if the neuron does not initially fire, for example, the system may remain in a steady state and not oscillate).
+The main function of the code calculates the left-hand side of Eq.
+1 of the system of differential equations which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.
+This procedure is followed by the ODE solver which solves the trajectory of the system given some initial conditions; for example, if the neuron does not initially fire, the system may remain in a steady state and not oscillate.
 
@@
 
-We realize the network shown in \Fref{fig: cpg} into a system of ODEs, and solve it.
+We construct the network shown in \Fref{fig: cpg} with a system of ODEs, and solve it.
 The equations are integrated, giving a timeseries of neuronal potentials.
@@
 Each neuron is attached to a muscle; when it fires, it causes the attached muscle to contract.
-We model the muscles as leaky integrators of the neuron's voltage; therefore, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.
+We model the muscles as leaky integrators of the neuron's voltage.
+In this model, muscles can be seen as “leaky integrators” (Boyle et al.
+2012) – the movement is heavily dependent on the current state of the neuron but is also dependent somewhat on the history.
+As a result, Gaussian smoothing of the neuron's voltage works to ``create'' an effective muscle contraction signal.
 Through Gaussian smoothing, the movement is heavily dependent on the current state of the neuron but also dependent somewhat on the history.
@@
 
-In this model, muscles can be seen as “leaky integrators” (Boyle et al. 2012) – the movement is heavily dependent on the current state of the neuron but is also dependent somewhat on the history.
-
 % TODO:
@@
 
-\subsection{Comparison to real worm}
+\subsection{Model versus Experimental Results}
 
@@
 While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos.
-It is not hard to see that a fully unconstrained worm might behave much like our model does.
-
+It can be seen that under the constraints of friction and other real-world conditions, the worm's range of motion is somewhat decreased.
+If these constraints were removed, the muscles of the worm would be able to contract fully and thus produce behaviour much like our model does.
 The worm undulates in a sinusoidal manner, both in simulation and reality.
@@
     \caption{A "dashboard view" representing the neuron and worm.
-(a) shows the potentials of the ventral neurons, coloured by number running down the worm.
-(b) shows "images" of the simulated worm at different timepoints.
+(a) shows the potentials of the ventral neurons, colored by number running down the worm.
+(b) shows "images" of the simulated worm at different times.
 The worm was simulated by running the neuron potentials through a Gaussian filter to simulate muscle dampening, then taking the amplitude as an angular displacement, representing contraction or relaxation.
@@
 Nagumo's tunnel diode exhibits this behaviour, but it may be replaced by any device with a similarly nonlinear V-I curve.
-The necessary feature is that in the oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
+The necessary feature consists of an oscillatory regime, the system is a relaxation oscillator, and that it has an excitable regime.
 
@@
 
-As a result of the piecewise linear approximation to the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.
-However, in experiments this did not cause a significant change in the dynamics of the individual neuron, or many connected together - the nullclines are sufficiently similar that the dynamics are effectively the same.
+As a result of the piecewise linear approximation of the cubic, the nullclines of the circuit system differ slightly from the original FitzHugh-Nagumo nullclines.
+However, in experiments this did not cause a significant change in the dynamics of the individual neuron, or many neurons connected together.
+The nullclines are sufficiently similar that the dynamics are effectively the same.
 
@@
 If each individual circuit is thought of as a single neuron, then we implemented diffusive coupling methods between those neurons.
-We also found that you don't need separate power supplies, and you can get finer control by adjusting the bias voltage and input through a separate mechanism.
+In that context, we found that you don't need separate power supplies, and you can get finer control by adjusting the bias voltage and input through a separate mechanism.
 
@@
     \inputtikz{figures/neuron_unit/neuron_unit}
-    \caption{The circuit we created, based of \citet{keener1983}.
-Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit looks more complex, in practice it is quite simple to implement.}
+    \caption{Our circuit, which is based of \citet{keener1983}.
+Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit might look more complex, in practice it is straight forward to implement.}
     \label{fig: neuron_unit}
@@
 
-However, this is only one neuron.
-In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.
+ In order to expand from a single neuron to a full central pattern generator, we implemented diffusive coupling mechanisms.
 These mechanisms are shown in \Fref{fig: coupling}.
-We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).
+We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$, the diffusion coefficient), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).
 The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.
@@
 
-To compare the analog implementation with our simulated model, we will focus on the timeseries output of the neurons, and not on the end worm.
-Include the relevant figure here - you can see clearly that the effect is the same.
-There are some differences in the waveform because of the different activation function in the circuit (linear interpolation).
+To compare the analog implementation with our simulated model, we will focus on the timeseries output of the neurons, and not on the end state worm.
 
@@
     \includegraphics[height=9cm]{figures/anal_sim_comp/anal_sim_comp.pdf}
-    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).
+    \caption{Comparison between computationally simulated dynamics (top row) and observed dynamics in the analog circuit (bottom row).
 (a) is the nullcline for the FitzHugh-Nagumo (simulated) equations, (b) is the "head oscillator" simulated (two neurons which mutually inhibit each other), (c) is the "descending pathway" simulated (one neuron driving another).
@@
 \end{figure}
+
+Looking at \Fref{fig: anal_sim_comp},
 

### 2020-12-27 paper.tex
fix some small problems
Changes from paper review

@@
 
-    The small (1 mm) nematode \emph{Caenorhabditis elegans} \cite{corsi2015} has become widely used as a model organism; in particular the \emph{C.
+    The small (1 mm) nematode \emph{Caenorhabditis elegans} (see wormbook.org) has become widely used as a model organism; in particular the \emph{C.
 elegans} connectome has been completely mapped, and \emph{C.
@@
 Our CPG model can be interpreted as having a graph-like structure, and it is easy to manipulate the "weights" of the edges (connections between neurons) of this "graph" to study defects or other changes in the CPG in an efficient, reproducible and explainable way.
+Additionally, the simplicity of the model means that it is easy, given a set of parameters, to investigate and reason about the reason for some behaviour of a worm.
+Since conditions in the lab are not exactly controllable, our model allows for the
 
@@
 We show later that breaking the symmetry of the CPG model can lead to radical changes in behaviour.
-
+\setcounter{figure}{1}
 \begin{figure}[h!]
@@
         \frac{dv}{dt} &= f(v) + w + I_\mathrm{ext}\\
-        \frac{dw}{dt} &= \varepsilon(v - \gamma w + \alpha )\\
+        \frac{dw}{dt} &= \varepsilon(v - \gamma w + \alpha)\\
         f(v) &= \frac{v^3}{3} - v
@@
     % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
-    \caption{Dynamics of \textit{C. elegans} neurons following Xu \textit{et al.} \cite{xu2018} (left )and Fitzhugh-Nagumo neurons \cite{fitzhugh1955, nagumo1962} (right).}
+    \caption{Dynamics of \textit{C. elegans} neurons following Xu \textit{et al.} \cite{xu2018} (left) and Fitzhugh-Nagumo neurons \cite{fitzhugh1955, nagumo1962} (right).}
 \end{figure}
@@
     \begin{aligned}
-        \frac{dv}{dt}   &= f(v) + w  + \color{green}{D(Δv)}\\
-        \frac{dw}{dt}   &= ϵ(a - bv)\\
+        \frac{dv}{dt}   &= f(v) + w  + \color{black}{D(Δv)}\\
+        \frac{dw}{dt}   &= \varepsilon (v - \gamma w + \alpha)\\
         f(v) &= \frac{v^3}{3} - v
@@
 
-We performed the simulations in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here
+% Structure:
+% - Describe the model, how the neurons are interconnected,
+%   as well as how the model in general functions (as 
+%   a function which solves a system of ODEs)
+% - Describe how the code works, in stages:
+%    - Initialize parameters
+%    - Integrate the solution to the system of DEs
+%    - Simulate the muscle response using smoothing
+%    - Construct the worm's shape using splines with the angle approach
+%
+% Basically, say enough that someone could replicate the idea without seeing the code at all.
 
-The main function of the code calculates the left-hand side of Eq.
-1 of the system of differential equations which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.
+We performed the simulations in Python, using the standard SciPy ODE solvers, which wrap LSODA, the Livermore Solver for Ordinary Differential Equations. % TODO list solver here
+
+The main function of the code solves the FitzHugh-Nagumo equations of \Fref{eq: fhnd}, having one set of such equations per neuron, which is materialized from our CPG connectome, when given the state and a set of unchanging parameters.
 This procedure is followed by the ODE solver which solves the trajectory of the system given some initial conditions; for example, if the neuron does not initially fire, the system may remain in a steady state and not oscillate.
 
-\subsection{Methods}
+\subsection{Overview of the methods}
+
+We are outlining the code here, but the full code can be found at *** add clean github link here ***.
 
@@
 
-\subsection{Generating undulation from neuron potential}
+\subsection{Initializing the model's parameters}
+
+% Mention that the FHN eqns are nondimensional and so all quantities have dimension but not units, i.e., arbitrary scaling.
+
+\subsection{Integrating the solution to the system of differential equations}
+
+\subsection{Simulating the worm's muscular response}
 
@@
 The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.
+
+\subsection{Constructing the worm's movement}
 
@@
     \caption{Comparison between computationally simulated dynamics (top row) and observed dynamics in the analog circuit (bottom row).
-(a) is the nullcline for the FitzHugh-Nagumo (simulated) equations, (b) is the "head oscillator" simulated (two neurons which mutually inhibit each other), (c) is the "descending pathway" simulated (one neuron driving another).
+(a) is the nullcline for the FitzHugh-Nagumo (simulated) equations, with the straight line being the $w$-nullcline and the cubic-like line being the $v$-nullcline; (b) is the "head oscillator" simulated (two neurons which mutually inhibit each other); (c) is the "descending pathway" simulated (one neuron driving another).
 (d) is the nullcline for the analog circuit - a piecewise linear approximation to the cubic, (e) is the analog version of the head oscillator, and (f) is the analog version of the descending pathway.}

### 2020-12-30 paper.tex
minor changes

@@
 generalized diffusion coupling between FHN neurons to model gap junctions and synapses.
-The effect of gap junctions and synapses upon the membrane potential is modeled by replacing the external current $I_\mathrm{ext}$ of the system, by a generalized diffusion term $D \max(Δv,0)$.
+The effect of gap junctions and synapses upon the membrane potential is modeled by replacing the external current $I_\mathrm{ext}$ of the system, by a generalized diffusion term, $D \max(Δv,0)$.
 A positive diffusion coefficient $D$ is used to simulate a gap junction, or an excitatory synapse and a negative coefficient to simulate an inhibitory synapse (\citet{collins1994}).

### 2021-01-01 paper.tex
Add more info on the process of simulation

@@
 % Mention that the FHN eqns are nondimensional and so all quantities have dimension but not units, i.e., arbitrary scaling.
+We have used the FitzHugh-Nagumo equations for our model neurons; these equations are completely non-dimensional, meaning that their scaling is arbitrary.
+As such, the constants, parameters, results, et cetera which we use have no units, and do not directly correspond to physical realities.
+
+For a CPG model, each individual neuron has a set of parameters $\left\{α, γ, ε\right\}$ and each connection has a diffusion coefficient associated with it.
+Additionally, it is easy to inject a current into a specific neuron, or to change a specific neuron's input requirements.
+
+In short - each neuron in the CPG has two inputs from other neurons (the preceding neuron in the chain driving it, and the opposite neuron inhibiting it).
+
+As such, there are five principal parameters per neuron: $α,\ γ,\ ε,\ D_\mathrm{desc},$ and $D_\mathrm{opp}$.
+$D_\mathrm{desc}$ is the diffusion coefficient corresponding to the neuron directly before, and on the same side as, the ``current'' neuron.
+Similarly, $D_\mathrm{opp}$ is the diffusion coefficient corresponding to the neuron on the opposite side of the nematode (dorsal or ventral).
+
+These parameters are passed as an array to the function which solves the differential equation.  See ***Appendix A*** for parameter values which worked for us.
 
 \subsection{Integrating the solution to the system of differential equations}
+
+Integration is done by a standard differential equation solver.
+To use the SciPy/LSODA interface, the function must take as input three objects $u,\ p,\ t$.
+Here, $u$ is the current state of the system (the values of $v$ and $w$ for each neuron), $p$ is the set of parameters for the system (in our case, all $α,\ γ,\ ε,\ D_\mathrm{desc},$ and $D_\mathrm{opp}$ per neuron) and $t$ is the time (which we do not use, since our DEs do not depend on time).
+
+The function must then return an array $du$, containing the derivatives $dv$ and $dw$ from each neuron.
+In our program, we have structured this so that systems are grouped together, that is, the array looks like $\left[dv_1, dw_1, dv_2, dw_2, ..., dv_i, dw_i\right]$.
+
+The function we have written is structured such that the parameters and state are ``unpacked'' from input arrays first, and then the equations are solved.
 
@@
 
+Essentially, the process is that
+
+\subsection{Constructing the worm's movement}
+
 Much like \citet{izquierdo2018} did, we take a segment-based approach to the worm model.
@@
 The magnitude of the “contraction” resulting from the smoothing is interpreted as an angular displacement for that segment.
-
-\subsection{Constructing the worm's movement}
 
